Interval-Valued Quantum Probabilities: Contextuality and the Born Rule

### 2017-05-25 prop_letter.tex
prop_letter.tex \section{Kochen-Specker} Simplify the proof a little bit
Updated by Prof. Hanson

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Fuzzy Measurements}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Intervals of Uncertainty}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Kochen-Specker}

@@

We will proceed by assuming a cryptodeterministic QIVMP $\bar{\mu}$
and derive a contradiction using the following nine ``Mermin-Peres square''
observables\nb\cite{Mermin1990Simple,peres1995quantum}:
\begin{center}
\begin{tabular}{|c|c|c|}
\hline 
$\mathbb{1}\otimes\sigma_{z}$  & $\sigma_{z}\otimes\mathbb{1}$  & $\sigma_{z}\otimes\sigma_{z}$ \tabularnewline
\hline 
$\sigma_{x}\otimes\mathbb{1}$  & $\mathbb{1}\otimes\sigma_{x}$  & $\sigma_{x}\otimes\sigma_{x}$ \tabularnewline
\hline 
$\sigma_{x}\otimes\sigma_{z}$  & $\sigma_{z}\otimes\sigma_{x}$  & $\sigma_{y}\otimes\sigma_{y}$ \tabularnewline
\hline 
\end{tabular}
\par\end{center}

@@

Since the expectation value\nb$\expval{\cdot}_{\bar{\mu}}$ satisfying
these two properties, the observables in the Mermin-Peres square must
have the the expectation value\nb$\left\{ 1\right\} $ or $\left\{ -1\right\} $.
In each row and column, operators commutes, and each operator is the
product of the two others, except in the third column $\left(\sigma_{z}\otimes\sigma_{z}\right)\left(\sigma_{x}\otimes\sigma_{x}\right)=-\sigma_{y}\otimes\sigma_{y}$.
Therefore, it is clear impossible to find a IVPM\nb$\bar{\mu}$ such
that 
\begin{equation}
\begin{aligned}\langle\mathbb{1} & \otimes\sigma_{z}\rangle_{\bar{\mu}} & \langle\sigma_{z} & \otimes\mathbb{1}\rangle_{\bar{\mu}} & \langle\sigma_{z} & \otimes\sigma_{z}\rangle_{\bar{\mu}}\\
\langle\sigma_{x} & \otimes\mathbb{1}\rangle_{\bar{\mu}} & \langle\mathbb{1} & \otimes\sigma_{x}\rangle_{\bar{\mu}} & \langle\sigma_{x} & \otimes\sigma_{x}\rangle_{\bar{\mu}}\\
\langle\sigma_{x} & \otimes\sigma_{z}\rangle_{\bar{\mu}} & \langle\sigma_{z} & \otimes\sigma_{x}\rangle_{\bar{\mu}} & \langle\sigma_{y} & \otimes\sigma_{y}\rangle_{\bar{\mu}}
\end{aligned}
\label{eq:MerminSquare-values}
\end{equation}
satisfying Eq.~(\ref{eq:Kochen-Specker-Rules}).

@@

\begin{proof}~
\begin{itemize}
\item Since $\bar{\mu}(\mathbb{0})=\imposs$, we have $\mu(\mathbb{0})=0$.
\item Since $\bar{\mu}(\mathbb{1})=\necess$, we have $\mu(\mathbb{1})=1$.
\item For every event $P$, we have\begin{subequations}
\begin{eqnarray}
 &  & \pmeas\left(P\right)=0\Rightarrow\bar{\mu}(P)\subseteq\left[0,\delta\right]\\
 & \Rightarrow & \bar{\mu}(\mathbb{1}-P)=\left[1,1\right]-\bar{\mu}(P)\subseteq\left[1-\delta,1\right]\\
 & \Rightarrow & \pmeas\left(\mathbb{1}-P\right)=1=1-\pmeas\left(P\right)\textrm{ .}
\end{eqnarray}
\end{subequations}Similarly, when $\pmeas\left(P\right)=1$, we also
have $\pmeas\left(\mathbb{1}-P\right)=1-\pmeas\left(P\right)$.
\item Given a pair of orthogonal operators\nb$P_{0}$ and $P_{1}$, we
have $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\bar{\mu}(P_{0})+\bar{\mu}(P_{1})$.
Without loss of generality, there are two cases:
\begin{itemize}
\item If $\pmeas\left(P_{0}\right)=\pmeas\left(P_{1}\right)=0$, then\begin{subequations}
\begin{eqnarray}
 &  & \bar{\mu}(P_{0})+\bar{\mu}(P_{1})\subseteq\left[0,2\delta\right]\\
 & \overset{2\delta<1-\delta}{\Rightarrow} & \bar{\mu}\left(P_{0}+P_{1}\right)\cap\left[1-\delta,1\right]=\emptyset\\
 & \Rightarrow & \bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[0,\delta\right]\\
 & \Rightarrow & \pmeas\left(P_{0}+P_{1}\right)=0=\pmeas\left(P_{0}\right)+\pmeas\left(P_{1}\right)\textrm{ .}
\end{eqnarray}
\end{subequations}
\item If $\pmeas\left(P_{0}\right)=0$ and $\pmeas\left(P_{1}\right)=1$,
then\begin{subequations}
\begin{eqnarray}
 &  & \bar{\mu}(P_{0})+\bar{\mu}(P_{1})\subseteq\left[1-\delta,1\right]\\
 & \Rightarrow & \pmeas\left(P_{0}+P_{1}\right)=1=\pmeas\left(P_{0}\right)+\pmeas\left(P_{1}\right)\textrm{ .}
\end{eqnarray}
\end{subequations}
\end{itemize}
Therefore, we always have $\pmeas\left(P_{0}+P_{1}\right)=\pmeas\left(P_{0}\right)+\pmeas\left(P_{1}\right)$.
By induction, we have $\pmeas\left(\bigcup_{i=1}^{N}P_{i}\right)=\sum_{i=1}^{N}\pmeas(P_{i})$
for any mutually orthogonal events\nb$\left\{ P_{i}\right\} _{i=1}^{N}$. 
\end{itemize}
\end{proof}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Gleason}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section{Introduction}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section{Fuzzy Measurements}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section{Intervals of Uncertainty}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section{Kochen-Specker}

@@

We will proceed by assuming a cryptodeterministic QIVMP $\bar{\mu}$
and derive a contradiction using the following nine ``Mermin-Peres square''
observables $\mathbf{O}_{ij}$\nb\cite{Mermin1990Simple,peres1995quantum}:
\begin{center}
\begin{tabular}{|c|c|c|}
\hline 
$\mathbb{1}\otimes\sigma_{z}$  & $\sigma_{z}\otimes\mathbb{1}$  & $\sigma_{z}\otimes\sigma_{z}$ \tabularnewline
\hline 
$\sigma_{x}\otimes\mathbb{1}$  & $\mathbb{1}\otimes\sigma_{x}$  & $\sigma_{x}\otimes\sigma_{x}$ \tabularnewline
\hline 
$\sigma_{x}\otimes\sigma_{z}$  & $\sigma_{z}\otimes\sigma_{x}$  & $\sigma_{y}\otimes\sigma_{y}$ \tabularnewline
\hline 
\end{tabular}
\par\end{center}

@@

Since the expectation value\nb$\expval{\cdot}_{\bar{\mu}}$ satisfying
these two properties, the observables in the Mermin-Peres square must
have the the expectation value\nb$\left\{ 1\right\} $ or $\left\{ -1\right\} $.
In each row and column, operators commutes, and each operator is the
product of the two others, except in the third column $\left(\sigma_{z}\otimes\sigma_{z}\right)\left(\sigma_{x}\otimes\sigma_{x}\right)=-\sigma_{y}\otimes\sigma_{y}$.
Therefore, it is clear impossible to find a IVPM\nb$\bar{\mu}$ such
that $\langle \mathbf{O}_{ij}\rangle_{\bar \mu}$
%\begin{equation}
%\begin{aligned}\langle\mathbb{1} & \otimes\sigma_{z}\rangle_{\bar{\mu}} & \langle\sigma_{z} & \otimes\mathbb{1}\rangle_{\bar{\mu}} & \langle\sigma_{z} %& \otimes\sigma_{z}\rangle_{\bar{\mu}}\\
%\langle\sigma_{x} & \otimes\mathbb{1}\rangle_{\bar{\mu}} & \langle\mathbb{1} & \otimes\sigma_{x}\rangle_{\bar{\mu}} & \langle\sigma_{x} & %\otimes\sigma_{x}\rangle_{\bar{\mu}}\\
%\langle\sigma_{x} & \otimes\sigma_{z}\rangle_{\bar{\mu}} & \langle\sigma_{z} & \otimes\sigma_{x}\rangle_{\bar{\mu}} & \langle\sigma_{y} & %\otimes\sigma_{y}\rangle_{\bar{\mu}}
%\end{aligned}
%\label{eq:MerminSquare-values}
%\end{equation}
satisfying Eq.~(\ref{eq:Kochen-Specker-Rules}).

@@

\begin{proof}~ 
\begin{itemize}
\item Since $\bar{\mu}(\mathbb{0})=\imposs$, we have $\mu(\mathbb{0})=0$. 
\item Since $\bar{\mu}(\mathbb{1})=\necess$, we have $\mu(\mathbb{1})=1$. 
\item For every event $P$, we have\begin{subequations} 
\begin{eqnarray}
 &  & \pmeas\left(P\right)=0\Rightarrow\bar{\mu}(P)\subseteq\left[0,\delta\right]\\
 & \Rightarrow & \bar{\mu}(\mathbb{1}-P)=\left[1,1\right]-\bar{\mu}(P)\subseteq\left[1-\delta,1\right]\\
 & \Rightarrow & \pmeas\left(\mathbb{1}-P\right)=1=1-\pmeas\left(P\right)\textrm{ .}
\end{eqnarray}
\end{subequations}Similarly, when $\pmeas\left(P\right)=1$, we also
have $\pmeas\left(\mathbb{1}-P\right)=1-\pmeas\left(P\right)$. 
\item Given a pair of orthogonal operators\nb$P_{0}$ and $P_{1}$, we
have $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\bar{\mu}(P_{0})+\bar{\mu}(P_{1})$.
Without loss of generality, there are two cases: 
\begin{itemize}
\item If $\pmeas\left(P_{0}\right)=\pmeas\left(P_{1}\right)=0$, then\begin{subequations}
\begin{eqnarray}
 &  & \bar{\mu}(P_{0})+\bar{\mu}(P_{1})\subseteq\left[0,2\delta\right]\\
 & \overset{2\delta<1-\delta}{\Rightarrow} & \bar{\mu}\left(P_{0}+P_{1}\right)\cap\left[1-\delta,1\right]=\emptyset\\
 & \Rightarrow & \bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[0,\delta\right]\\
 & \Rightarrow & \pmeas\left(P_{0}+P_{1}\right)=0=\pmeas\left(P_{0}\right)+\pmeas\left(P_{1}\right)\textrm{ .}
\end{eqnarray}
\end{subequations} 
\item If $\pmeas\left(P_{0}\right)=0$ and $\pmeas\left(P_{1}\right)=1$,
then\begin{subequations} 
\begin{eqnarray}
 &  & \bar{\mu}(P_{0})+\bar{\mu}(P_{1})\subseteq\left[1-\delta,1\right]\\
 & \Rightarrow & \pmeas\left(P_{0}+P_{1}\right)=1=\pmeas\left(P_{0}\right)+\pmeas\left(P_{1}\right)\textrm{ .}
\end{eqnarray}
\end{subequations} 
\end{itemize}
\end{itemize}
\end{proof}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section{Gleason}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section{Conclusion}
